preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution

### 2020-09-28 Manuscript/manuscript.Rmd
simplify BioC availability
knit to word

---
title: "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution"
csl: styles.ref/genomebiology.csl
output:
  pdf_document: 
    extra_dependencies: ["float"]
  word_document:
    reference_docx: styles.doc/Arial_11_double_space_normal_margins.docx
bibliography: References/references.bib
---

>>>>

---
title: "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution"
csl: styles.ref/genomebiology.csl
output:
  word_document:
    reference_docx: styles.doc/Arial_11_double_space_normal_margins.docx
  pdf_document: 
    extra_dependencies: ["float"]
bibliography: References/references.bib
---
